### 2018-04-14 experiments.tex
edits

\subsection {Case Study: pyfakefs}

The {\tt pyfakefs} \cite{pyfakefs} module implements a fake file
system that mocks the Python file system modules, to allow Python
tests both to run faster by using an in-memory file system and to make
or depend on file system changes that would
not be safe or easily performed using real persistent storage.  Originally
developed in 2006 at Google by Mike Bland, {\tt pyfakefs} is now used
in over 2,000 Python tests, inside and outside Google.

We introduced a subtle bug into {\tt pyfakefs}, where the {\tt remove}
call checks that its target is not a directory, and returns the
correct error, but still carries out the remove operation.  Using {\tt
  os.remove} to delete directories does not break any file system
invariants, but violates the Python {\tt os} specification (and,
indirectly, the usual POSIX implementation behavior where {\tt unlink}
does not work for directories).  Detecting this bug using the TSTL
{\tt pyfakefs} harness is normally impossible without using another
file system as a reference.  However, the fault is detected
immediately, without using a reference, when we compile the harness
with the {\tt --checkFailureDeterminism} flag.

>>>>

\subsection {Case Study: {\tt pyfakefs}}

The {\tt pyfakefs} \cite{pyfakefs} module implements a fake file
system that mocks the Python file system modules, to allow Python
tests both to run faster by using an in-memory file system and to make
or depend on file system changes that would
not be safe or easily performed using real persistent storage.  Originally
developed in 2006 at Google by Mike Bland, {\tt pyfakefs} is now used
in over 2,000 Python tests, inside and outside Google \cite{pyfakefs}.

The TSTL harness for {\tt pyfakefs} has been used to detect (and
correct) over 50 faults.  However, the testing completely relies on
the existence of a reference POSIX implementation.

We introduced a subtle bug into {\tt pyfakefs}, where the {\tt remove}
call checks that its target is not a directory, and returns the
correct error, but still carries out the remove operation.  Using {\tt
  os.remove} to delete directories does not break any file system
invariants, but violates the Python {\tt os} specification (and,
indirectly, the usual POSIX implementation behavior where {\tt unlink}
does not work for directories).  Detecting this bug using the TSTL
{\tt pyfakefs} harness is normally impossible without using another
file system as a reference.  However, the fault was detected
immediately, even without using a reference, when we compile the harness
with the {\tt --checkFailureDeterminism} flag.
Moreover, the overhead for adding a check for failure determinism was
less than 8\%.
